DATA 621 - Business Analytics and Data Mining

### 2020-12-03 Final_project/Final Project Paper - Group 2.Rmd
Stopping for the night

@@

@@

There is no clean table of coefficients with elasticNet. Rather there is a
sequence of models built behind the scenes. The coefficients of the selected
model can be found in the appendix.

>>>>

What also seems counterintuitive at first are the negative correlations between
`lkratio` and `unan` being true with views. It may well be that conflict is good
for Youtube videos. Perhaps the more a video is talked about or argued over, the
more views it will get!

@@

This model has more predictors than does the simple Gaussian (G)LM, although
their signs are similar. What stands out is how many more categories were
considered significant.

@@

```{r lm3Table}
# The only way to extract the coefficients from an elastic net model in R
# Is to predict them using the optimal tuning values

lm3C <- predict(lm3$finalModel, s = lm3$finalModel$tuneValue[[1]],
                type = 'coefficients', mode = 'fraction')
lm3CC <- lm3C$coefficients[lm3C$coefficients != 0]
kable(lm3CC, digits = 3L, format.args = list(big.mark = ','),
      caption = 'Coefficients of "Optimal" Elastic Net Model')
```

There is no clean table of coefficients with elasticNet. Rather there is a
sequence of models built behind the scenes. The coefficients of the selected
model can be found through predicting them, but there are no corresponding
p- or Z-values. Worse, there is no intercept returned.

Nevertheless, the *relative* magnitude and sign of the parameters are in line
with our expectations. `Nonprofits & Activism` has the largest factor effect, to
the worse. Both `likes` and `dislikes` are positively correlated with views and
`comments` is negatively correlated. A few more categories join
`Film & Animation` as contributing to excess views over the baseline
`Entertainment`. Lastly, having a preponderance of likes tends to reduce views.
Conflict seems to be good for Youtubers!
